Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-08 automatica/paper.tex
wording: precision

Our work addresses challenging aspects of the control synthesis problem:  
we perform digital control synthesis over a ``hybrid model'',
namely a model encompassing a plant exhibiting continuous behavior, 
whereas the controller operates in discrete time and over a quantized domain.  
In particular, our model evaluates the effects of the quantizers (A/D and D/A
converters), as well as representation
errors introduced by working  %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite-precision domain. 
We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.

>>>>

Our work addresses challenging aspects of the control synthesis problem:  
we perform digital control synthesis over a ``hybrid model'',
namely a model encompassing a plant exhibiting continuous behavior, 
whereas the controller operates in discrete time and over a quantized domain.  
In particular, our model evaluates the effects of the quantizers (A/D and D/A
converters), as well as representation
errors introduced by the controller working  %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite-precision domain. Our model also accounts for representation errors introduced
by our modelling of the plant using finite precision arithmetic. 
We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.
